---
title: "Assignment 1"
---

# Assignment 1

```{r}
1 + 1
```

My first assignment has two parts.

## (a)

I choosed first video with Kerem Demirtaş.

Summary

Data science is used in many areas in the world such as healthcare, inventory management, and autonomous vehicles. Statistics is one of the main tools of data science. However, it is not possible to solve a problem only with model and algorithm knowledge if there is no understanding of the subject. For this reason, data science is not the same as artificial intelligence, and artificial intelligence cannot replace data science. In addition, the human factor is always important in data science processes.

The workflow of data science usually includes several steps: problem definition, data collection and data preparation, exploratory data analysis (EDA), model building and algorithms, evaluation, and finally production and monitoring of live performance. In this process, defining the problem clearly is very important.

The topic of this thesis is a road system where autonomous vehicles and human-driven vehicles travel together. The aim of this study is to guide autonomous vehicles in mixed traffic in order to achieve maximum efficiency.

1-Which one is Data Science?

a)  Glorified statistics

b)  Solve any problem

c)  Data Science does not equal AI

d)  All about big data

2-What is the first step of Data Science?

Answer Key:

1- C

2- Defining the problem correctly.

## (b)

```{r}
library(dslabs)
data(polls_us_election_2016)
head(polls_us_election_2016)

```

```{r}
my_first <- "Sila Nur Guney"
 my_birth_year <- "2002"
 cat("My first name is", my_first,"\n")
 cat("My birth year is", my_birth_year)
#cat komutu ai ile öğrenilmiştir.
```

```{r}
my_birth_year_sayi<-as.numeric(my_birth_year)

number_of_char<- nchar(my_first)
k <- (nchar(my_first) + my_birth_year_sayi) %% 15 + 8
print(k)

```

```{r}
birth_years<- 1995:2005
k_datas<- (nchar(my_first) + birth_years) %% 15 + 8

print(k_datas)


```

```{r}
if (k%% 2 == 0) {
  head(polls_us_election_2016, k)
} else {
  tail(polls_us_election_2016, k)
}
#Bu döngünün oluşturulmasında Ai'dan yardım alınmıştır.

```

```{r}
is.na(polls_us_election_2016)
sum(is.na(polls_us_election_2016))
#is.na fonksiyonu ai ile öğrenilmiştir.
```

```{r}
print(sum(is.na(polls_us_election_2016)))
```
